% Acknowledgement

I did not complete this work alone.
In my eleven years at Montana State I have had the opportunity to work with, and learn from, so many of you.
I hope I can acknowledge you all, but if I can't, thank you so much and I hope our paths continue to cross for years to come.

Thank you to C. Riedel, D. Longcope, J. Qiu, C. Kankelborg, J. Carlsten, and R. Babbitt, all of whom I have taken multiple physics courses from, for being supportive, always available, and fun to be around.
Thank you to the Physics staff, to N. Williams, M. Jarrett, and J. Bradley, for you support and friendship over the years.
Thank you to K. Mashburn and H. Courrier for teaching me how to build flight hardware.
Thank you to T. Rust for helping me through the frustrations of optical testing, focus, and alignment.
Thank you to S. Atwood for starting me down this road.
Thank you M. Johnson, N. Goldsworth, H. Moore, A. Tientze, J. Martinez, B. Carrol, and C. Bunn for helping to build and launch ESIS.
Thank you to the team at WSMR circa 2019, the Beabouts, H. Haight, and K. Kobayashi for all the assistance and knowledge you have shared with me and the ESIS team.
Thank you to D. Mckenzie for assisting as a committee member, even after leaving MSU, and to A. Winebarger, for working closely with me over the last year and always being available to help. 
Lastly to Roy Smart, thank you for all your help in the world of electronics and coding, and insistence on getting things right, and again to Charles, the opportunities and education you've provided me are immeasurable.
We made an amazing team, and accomplished something very cool.
I hope that doesn't end, and thank you.


 
	








